---
title: "Data 607 - Final Porject Proposal"
author: "Joseph Simone"
date: "11/15/2019"
output:
  html_document:
    toc: true
    theme: journal
    highlights: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r, message=FALSE, warning= FALSE}
library(jsonlite)
library(tidyverse)
library(tibble)
library(knitr)
```


## Data Management and Acquisition Final Project Proprosal 
## Mass and School Shooting in America Analysis

### Background
Not only is the topic of Gun Violence in America considered to be a $"hot"$ $"topic"$ for debate, the School and Mass Shooting epidemic in this country is one that can " hit slose to home" for most of us. During the research phase of this project, I could not decide whether I was going to focus just on $"School"$ related shooting or stick with $"Mass"$ shootings as a whole. Therefore, I'm going to use both for this analysis. Using the School Shooting Dataset as a subset of the overall Mass Shooting Dataset. Performing analysis along the way. For instances, one of these statistical measures can be, Which percent of mass shootings happen on K-12 School Campuses?

### Data Sources

##### Open Data Soft - Mass Shooting in America 
[linked phrase](https://public.opendatasoft.com/explore/dataset/mass-shootings-in-america/information/)

##### Center for Homeland Defense and Security - K-12 School Shooting Database 
[linked phrase](https://www.chds.us/ssdb/)


### Data Import & Initial Tidying
#### Mass Shooting Data 
```{r, message=FALSE, warning= FALSE}
json_mass_file <-"https://raw.githubusercontent.com/josephsimone/Data_607_Final_Project/master/mass-shootings-in-america%20(1).json"
```

```{r, message=FALSE, warning= FALSE}
yelp <- stream_in(file(json_mass_file))
```

```{r message=FALSE, warning= FALSE}
yelp_flat <- flatten(yelp)
str(yelp_flat)
yelp_tbl<-as.data.frame(yelp_flat)
```

```{r message=FALSE, warning= FALSE}
mass_tbl<-as_tibble(yelp_tbl)
```

#### School Shooting Data 
```{r, message=FALSE, warning= FALSE}
school_file <- read_csv(file ="https://raw.githubusercontent.com/josephsimone/Data_607_Final_Project/master/K-12%20SSDB%20(Public)%20-%20K-12%20SSDB%20(Public)%20Linked.csv")
```

```{r}
head(school_file)
```


```{r}
colnames(school_file) = school_file[1, ]
```

```{r}
colnames(school_file) = school_file[1, ]
school_file = school_file[-1, ]
```


```{r}
head(school_file)
```

